Convex Surrogates via Polyhedral Losses

### 2019-04-29 neurips-19/cvx-fin.tex
Jessie small edits and questions

Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds,\raft{TODO: prove this :-]}
thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.

We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
Our results give a complete characterization in the case of dimension 1, that is, real-valued surrogates.
We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
We conclude with preliminary results in higher dimensions and other future directions.

@@

For the case of $\reals^2$, we will show that no embedding can do better.

@@

  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method.

@@

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}

@@

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

@@

\begin{definition}[Separated Link]\label{def:links}
  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
  A \emph{link function} is a map $\psi:\reals^d\to\R$.
  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
  \begin{align*}
    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
  \end{align*}
  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
\end{definition}

>>>>

Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds, \raft{TODO: prove this :-]}
thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.

We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
We conclude with preliminary results in higher dimensions and other future directions.

@@

For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better.

@@

  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method. \jessiet{In what sense do they not consider embedding?  The formalism we present?  They intuitively embed into the reals, but I don't remember if they focus on polyhedral losses}

@@

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\jessiet{Do we want }

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.}

@@

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
\jessiet{Do we want to mention $r \to$ discrete reports and $u \to$ real reports?}

@@

\begin{definition}[Separated Link]\label{def:links}
  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
  A \emph{link function} is a map $\psi:\reals^d\to\R$.
  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
  \begin{align*}
    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
  \end{align*}
  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
  \jessie{Where does $\delta$ being a constant come from?  In \citet{ramaswamy2018consistent} bottom of Section 2, $\xi$ is a monotonic, continuous function, not a constant.  We also have $\delta$ on the other side of the inequality that they have $\xi$ on, but I think that will be okay?}
\end{definition}
